Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-04-01 src-latex/parts/10-introduction.tex
Add section 3
WIP rebuttal
Ref to fig. 1 + mention to thumbnails
Move fig. 1 ref from abstract to introduction
Relecture globale et correction de coquilles

% !TeX root = ../main-paper.tex
\begin{figure}[!h]
    \centering
    \includegraphics[width=.9\textwidth]{figs/overview-intro.pdf}
    \caption{%
    Overview of the pipeline under study.
    From previously-extracted images of directory entries, 
    we perform OCR and named entity recognition (NER) using different techniques.
    We aim at answering the following questions:
    \emph{How noisy are modern, out-of-the-box OCR systems?}
    \emph{What is the behaviour of NER when OCR is noisy?}
    \emph{Can NER be made more robust to OCR noise?}
    }
    \label{<label>}
\end{figure}
\clearpage% force float flush!

@@

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due to multiple causes related to text readability (low resolution scans, inconsistent printing rules, artefacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the great diversity of historical sources.
On the other hand, the semantics of entities in NER approaches developed for modern texts may be different from those in ancient texts.

@@

Trade directories have been leveraged in recent work to identify polluted urban soils \cite{bell2020automated} and locate all gas stations in the city of Providence over the last century.
In an ongoing research project, we aim at producing structured spatio-temporal data from the entries of the Paris trade directories to study the dynamics of the fraction of the the XIX\textsuperscript{th} century Parisian society reachable through these sources.
%Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
Therefore, we investigate several state-of-the-art OCR and NER approaches to assess their usability to process the corpus.

The contributions of this article are as follows:
% Contributions
\begin{enumerate*}[(i)]
    \item We review state-of-the-art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformed-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}

>>>>

% !TeX root = ../main-paper.tex
\begin{figure}[!h]
    \centering
    \includegraphics[width=.9\textwidth]{figs/overview-intro.pdf}
    \caption{%
    Overview of the pipeline under study.
    From previously-extracted images of directory entries, 
    we perform OCR and named entity recognition (NER) using different techniques.
    We aim at answering the following questions:
    \emph{How noisy are modern, out-of-the-box OCR systems?}
    \emph{What is the behaviour of NER when OCR is noisy?}
    \emph{Can NER be made more robust to OCR noise?}
    }
    \label{fig.pipeline-overview}
\end{figure}
\clearpage% force float flush!

@@

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due to multiple causes related to text readability (low resolution scans, inconsistent printing rules, artefacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts and special glyphs) and the variability inherent to the great diversity of historical sources.
On the other hand, the semantics of entities in NER approaches developed for modern texts may be different from those in ancient texts.

@@

Trade directories have been leveraged in recent work to identify polluted urban soils \cite{bell2020automated} and locate all gas stations in the city of Providence over the last century.
In an ongoing research project, we aim at producing structured spatio-temporal data from the entries of the Paris trade directories to study the dynamics of the fraction of the XIX\textsuperscript{th} century Parisian society reachable through these sources.
%Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
Therefore, we investigate several state-of-the-art OCR and NER approaches to assess their usability to process the corpus (\cref{fig.pipeline-overview}).

The contributions of this article are as follows:
% Contributions
\begin{enumerate*}[(i)]
    \item We review state-of-the-art OCR and NER systems for historical documents (\cref{sec:related-work}).
    \item We introduce a new dataset suitable for OCR and NER evaluation (\cref{sec:dataset}).
    \item We measure the performance of three modern OCR systems on real data (\cref{sec:ocr-xp}).
    \item We evaluate modern NER approaches: their requirements in terms of training data, and the effects of pre-training (\cref{sec:ner-xp1}).
    \item We show that Transformer-based NER can benefit from pre-training and fine-tuning to improve its performance on noisy OCR (\cref{sec:ner-xp2}).
\end{enumerate*}
